---
title: "SimplifyStats Vignette"
author: "Zachary Colburn"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

*SimplifyStats* provides a set of functions to simplify the process of 1) generating descriptive statistics for the numeric variables of multiple groups and 2) performing hypothesis testing between all combinations of groups.

## Generate group-wise descriptive statistics

The function **group_summarize** can be used to generate descriptive statistics for multiple groups based on unique combinations of the grouping variables.
```{r}
library(SimplifyStats)

# Generate data.
df <- iris

# Modify df to demonstrate additional functionality.
## Add an NA.
df$Sepal.Length[1] <- NA
## Add another grouping variable.
df$Condition <- rep(c("untreated","treated"), 75)

# Generate descriptive statistics.
group_summarize(
  df, 
  group_cols = c("Species","Condition"), 
  var_cols = c("Sepal.Length","Sepal.Width"), 
  na.rm = TRUE
)
```

## Perform pair-wise hypothesis testing
Similarly, the function **pairwise_stats** can be used to perform pairwise statistical tests for multiple variables based on unique combinations of the grouping variables.
```{r}
# Generate descriptive statistics.
pairwise_stats(
  df, 
  group_cols = c("Species","Condition"), 
  var_cols = c("Sepal.Length", "Sepal.Width"),
  t.test
)
```
